Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2015-02-21 doc/GMP2015/revision_1/appendix_proofs.tex
Finished and submitted revision 1.

\section{Proofs}
\label{sec:appendix:a}

@@

\newcommand{\usestwod}{\todo{Uses 2D requirement:}}
\renewcommand{\usestwod}{}

\subsubsection{Proof of Theorem \ref{theorem:main}}\label{theorem:main:proof}

\begin{proof}
We show the existence of a canonical DR-plan by constructing it as follows:

Begin with $\comdrp{G}$ of a rigid 2D bar-joint graph $G$, for all nodes $C$
with children $C_1,\ldots,C_N$ keep children nodes according to the following rules:
\begin{enumerate}
   \item If $C_i \cap C_j$ is trivial then keep all $C_1,\ldots,C_N$ as children.
   \item If $C_i \cap C_j$ is rigid then select any two out of $C_1,\ldots,C_N$ as children.
\end{enumerate}

This directly satisfies properties 2 and 3 of a canonical DR-plan (see definition \ref{def:canonical_drplan}), because all the nodes in $\comdrp{G}$ are rigid vertex-maximal proper subgraphs. However, we still have to show property 1 (that this makes a DR-plan).
For rule (1), because we are beginning with a complete DR-plan, if we keep all the children it is still a DR-plan. For rule (2), we know that the union must be rigid as well and it cannot be anything other than $C$, otherwise we have found a larger rigid vertex-maximal proper subgraph.

If we begin with an isostatic graph, rigid can be replaced with isostatic throughout the construction and remain valid. The rigid proper subgraphs of an isostatic graph must be isostatic themselves.

Now we must show that a canonical DR-plan is optimal. The proof is by induction on the level of the plan; we show that following these rules always guarantees minimum fan-in at this level and does not increase fan-in on following levels.

 % We do this inductively on the l, beginning with the root node, showing that the rules are always the optimal choice.
% by discussing each rule and proving inductively that this is the optimal choice at each level of the DR-plan tree, starting with the root node.

% Now we show that this plan is optimal by considering the two cases. Observation \ref{lemma:union_intersection} shows that we do not have to consider anything other than the two cases stated in the construction.
 % the intersection of any two isostatic subgraphs can only result in trivial or isostatic subgraphs. Therefore, given $C$ and its isostatic vertex-maximal subgraphs $C_1,\ldots,C_N$, the are only two possibilities to consider. Either (1) subgraphs $C_i$ and $C_j$ have a trivial intersection, or (2) they have an isostatic intersection.

\medskip\noindent
\vemph{Rule 1:}
% If some pair is intersecting trivially, then in fact all pairs intersect trivially, thus all must be children by defn of canonical drplan
%
First, we claim that if the intersection is trivial all $C_1,\ldots,C_N$ must be children of $C$ in an optimal DR-plan. We do this by showing that no subset of the children can union to form $C$, thereby requiring all of them be included; because this is the only choice, it is the minimum fan-in any DR-plan could have for this node.
% must be optimal for this node.

Take the strict subset $S\subsetneq \{1,\ldots,N\}$ such that $U=\bigcup_{i\in S}{C_i}$ which we \vemph{assume} is isostatic. If $U\neq C$, then we just found a larger proper subgraph and the children were not vertex-maximal to begin with. So, it must be that $U=C$.
\usestwod
However, since $C_i \cap C_j$ is trivial then for $k\notin S$ we know, by Lemma \ref{lemma:combined_lemma}, point \ref{lemma:uc_intersection_makes_all_uc}, $U\cap C_k$ must be one or more trivial subgraphs. By definition of a DR-plan $C_k=C\cap C_k$ and we know that $U=C$ so $C_k=U\cap C_k$. Thus, $C_k$ is both one or more trivial subgraphs and a isostatic subgraph of $C$. Thus, the assumption is wrong and $U$ cannot be isostatic. As $C$ is isostatic, this means no proper subset of $C_1,\ldots,C_N$ can union to form $C$.

Furthermore, since a canonical DR-plan uses proper rigid \vemph{vertex-maximal} subgraphs as children, and because their pairwise intersection is trivial, it follows that any such node has at most as many children as a DR-plan without this restriction, because the union of the children have to contain all edges of the parent. Therefore, this is the optimal choice in this case.

\medskip\noindent
\vemph{Rule 2:} Second, we claim that if the intersection is isostatic, the choice of any two children will result in an optimal DR-plan.

If $C_i \cap C_j$ is isostatic, then, by Observation \ref{lemma:union_intersection}, $C_i \cup C_j$ is also isostatic. This means that, by Lemma \ref{lemma:combined_lemma}, point \ref{lemma:wc_intersection_makes_all_wc}, any two children of $C$ will union to $C$ itself. Thus, any two children can be chosen to make a canonical DR-plan.
% are potential choices for the optimal DR-plan as they all create equal fan-in (exactly two) at this level.

\newcommand{\induceonc}[1]{Idc\left(C,#1\right)}
\renewcommand{\induceonc}[1]{#1}
\newcommand{\iunion}[1]{\induceonc{I\cup\bigcup_{k\in S_N\setminus\{#1\}}{R_k}}}

However, to guarantee that any two are the \vemph{optimal} choice, it must ensure minimum fan-in over all descendants. Take the set $S_N=\{1,\dots,N\}$, then we call $I=\bigcap_{k\in S_N}{C_k}$ and $R_k=C\setminus C_k$. Suppose we select $i$ and $j$, where $i\neq j$, as the children. For convenience, we will assume all subgraphs are induced subgraphs on $C$. We know that $C=\induceonc{I\cup\bigcup_{k\in S_N}{R_k}}$ and $C_i=\iunion{i}$. The isostatic vertex-maximal subgraphs of $C_i$ are $(\iunion{i,1}),\ldots,(\iunion{i,i-1}),(\iunion{i,i+1}),\ldots,(\iunion{i,N})$ all of which intersect on isostatic subgraphs. So any two of these are viable children for $C_i$.
% Since
% \[C_i=Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i\}}{R_k}\right)\]
% the children of $C_i$ will be
% \[Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,m\}}{R_k}\right)\]
% and
% \[Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,n\}}{R_k}\right)\]
% % $C_i=Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i\}}{R_k}\right)$
% % the children of this node will be
% % $Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,m\}}{R_k}\right)$
% % and
% % $Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,n\}}{R_k}\right)$
% for arbitrary $m$ and $n$, where $i,j,m,n$ do not equal each other. \todo{Prove these are valid children? Or is this obvious?}
This continues for $N-1$ levels total, always with fan-in of two (the minimum possible), at which point every descendant of $C$ is some $\induceonc{I\cup R_k}$ for $k\in S_N$, with every $k$ appearing at least once. Thus, regardless of the choice of $C_i,C_j$, then their children, etc., the DR-plan has fan-in of two for every node for the next $N$ levels, at which point the nodes contain the same subgraphs. Therefore, the choice is optimal.
%
% \medskip\noindent
% This proof then applies to itself recursively to show that the fan-in of the children will also be minimum.
%
% -- say this at top `proof is by induction on the level of the dr=plan'
\end{proof}

@@

For (4), because subgraphs of a isostatic graph can only be trivial, under-, or isostatic, all cases have already been exhausted.
\end{proof}

@@

For convenience, it is implied that all graphs are the induced graph on $C$.
\newcommand{\inducedOnC}[1]{#1}

% \newcommand{\inducedOnC}[1]{Idc\left(C,#1\right)}

@@

\subsubsection{Proof of Theorem \ref{theorem:algo_complexity}}

\begin{proof}
The first step of the algorithm is finding the isostatic vertex-maximal proper subgraphs of the input isostatic graph $G$. Do this by first dropping arbitrary edge $e$ from the edge set and running the pebble game algorithm \cite{Jacobs:1997:PG} on this subgraph, which is $O(|V|^2)$. The output of this will be a list of component-candidates. Then run the Frontier algorithm \cite{hoffman2001decompositionII} \cite{lomonosov2004graph} ($O(|V|)$) on each candidate along with edge $e$, which will find the minimal subgraph $D$ that contains the candidate and $e$. If $D=G$, move the candidate (before adding $e$) to the true-component list and remove it from the candidate-component list. If $D\subsetneq G$, remove all candidates that are subgraphs of $D$ from the candidate-component list and add $D$ back to the list. Continue with the next candidate. When you exhaust the candidates, move to the next step.

Test the intersection of any two of the true-components. If the intersection is trivial, the entire list becomes the children. Recursively apply the algorithm to each child.

If the intersection is non-trivial (necessarily isostatic), immediately compute the sequential decomposition down to $I=\bigcap_{k\in S_N}{C_k}$. The root of this idea is discussed in detail in the proof of Theorem \ref{theorem:main}, and we use the notation here. We construct a DR-plan whose node set is the same as that of a canonical/optimal DR-plan. Begin with the parent $C$. Its children will be $C\setminus R_1$ and $R_1$ plus the nodes and edges adjacent to $R_1$ that lie in $I$. Recursively apply the algorithm to the child containing $R_1$. The children of $C\setminus R_1$ will be $C\setminus (R_1\cup R_2)$ and $R_2$ plus the nodes and edges adjacent to $R_2$ that lie in $I$. And so on. At $N$ levels down, the 2 children will be $I$ and $R_N$ plus the nodes and edges adjacent to $R_N$ that lie in $I$. Apply the algorithm recursively to both children.
% Although the nodes containing $R_1,\ldots,R_N$ are underconstrained, simply take the children to be the roots of the forest

The reason for this construction is that the result is a tree with no duplicate nodes. The leaves of this tree will exactly be the edges of this graph. Therefore, the number of nodes in the tree is $O(|E|)$ which, for isostatic input graphs, is $O(|V|)$.

Therefore, the complexity of the algorithm as a whole is $O(|V|^3)$.
%
% \note In the best case, this can be $O(V^2)$ if the graph is a 2-tree
\end{proof}

% \begin{proof}
% The first step of the algorithm is finding the isostatic vertex-maximal proper subgraphs of the input isostatic graph $G$. Do this by first dropping arbitrary edge $e$ from the edge set and running the pebble game algorithm \cite{Jacobs:1997:PG} on this subgraph, which is $O(|V|^2)$. The output of this will be a list of component-candidates. Then run the Frontier algorithm \cite{hoffman2001decompositionII} \cite{lomonosov2004graph} ($O(|V|)$) on each candidate along with edge $e$, which will find the minimal subgraph $D$ that contains the candidate and $e$. If $D=G$, move $D$ to the true-component list and remove the candidate from the candidate-component list. If $D\subsetneq G$, check the union of $D$ with the all items in the true-component list; if the union is isostatic, halt and output just these two components as children. Otherwise, remove all candidates that are subgraphs of $D$ from the candidate-component list and add $D$. Continue with the next candidate. If you exhaust the candidates, output the entire true-component list.

% %on the children
% This is run recursively on each node. If you use dynamic programming to store the decompositions of each component, it prevents repetition of work (done by using the DAG representation of the DR-plan). In this case you will have to do work on no more than $O(|V|)$ nodes that get smaller at each level.

% Thus, the running time is at most $O(|V|^3)$. \todo{does this amortize correctly?}

% It's a tree in only trivial case -> O(V), always order of leaves
% If its isostatic intersection, we do the sequential extension,intersections only done once.

% inductively. The number of nodes at this level will e more than the total. Number of leaves (terminals for dag) is at most the number of edges

% \end{proof}

% \begin{proof}
% The first step of the algorithm to find an optimal DR-plan is the most difficult --- to find the wellconstrained vertex-maximal proper subgraphs of the input wellconstrained graph. There are two approaches: (1) the bottom-up approach, using the Frontier algorithm \cite{Oung:2001:FFE:376957.376995} to grow these components from single vertices; and (2) the top-down approach, using the pebble game algorithm \cite{Jacobs:1997:PG} on each node and taking the largest components that are not subgraphs of any larger ones. After the subgraphs have been found, it is a straightforward application of the theory. If the intersection of any two of the subgraphs is wellconstrained, then take those two to be children of the graph. Otherwise, all the subgraphs are the children. Apply recursively to the children. This naturally terminates when you reach trivial subgraphs. The complexity of this depends on the algorithm for finding children (both are polynomial) and the depth of the plan (the deeper the plan, i.e.\ the smaller the max fan-in, the longer the running time). \todo{Think more about complexity.}
% \end{proof}

@@

\subsubsection{Proof of Theorem \ref{theorem:omdk}}
\begin{proof}
The proof follows from the fact that 2-trees are well decomposable and
have simple DR-plans of size 2. We know that $G$ can be reduced by
removing $k$ edges to create a partial-2-tree $G'$ which can then be
completed to an (isostatic) 2-tree by adding some set of non-edges
$F$. Thus the modified graph $H = G'\cup F$ has  a DR-plan of size 2,
proving the theorem.
\end{proof}

\subsubsection{Proof of Theorem \ref{theorem:criterionc}}
\begin{proof}
    The Cartesian realization space of $(H,\left<\delta_{E'},
    \lambda_F\right>)$ is computed easily with a DR-plan of size 2,
    and is the union of $2^t$ solutions (modulo orientation preserving
    isometries) each with a distinct orientation type, where $t$ is
    the number of triangles in the 2-tree $H$; here $\delta_{S}$ is
    the restriction of the length vector $\delta$ to the edges in $S$.
    A desired solution $p$ (or connected component of a solution
    space) of $(G,\delta)$ of an orientation type $\sigma_p$ can be
    found by a subdivided binary search   of the cartesian realization
    space of $(H, \left<\delta_{E'}, \lambda_F\right>)$ of orientation
    type $\sigma_p$ - as $\lambda_F$ ranges over the discretized
    convex polytope $\Phi_F(G',\delta_E')$ with bounding hyperplanes
    described in Theorem \ref{theorem:convexcayley}. A solution $p$
    is found  when the lengths for nonedges in $D$ match $\delta_D$.
\end{proof}

@@

\subsubsection{Proof of Remark \ref{thm:1dofcase}}
\begin{proof}
    Suppose we are given a body-pin graph and its corresponding body-bar graph $G$ and have obtained the 1-dof DR-plan $T$. Each node of $T$ will then be a vertex maximal proper 1-dof sub-graph of $G$.

@@

\begin{proof} %[Proof of Lemma~\ref{lemma:wc_intersection_makes_all_wc} for 2D pinned line incidence graphs]
We use the same notations as in the original proof of Lemma \ref{lemma:combined_lemma}, Point \ref{lemma:wc_intersection_makes_all_wc}, in the last section.

@@

Then we analyze all the possible cases for $C_k$.
\begin{itemize}
    \item 1 case: $C_k=Idc(C,R'_i\cup R'_j\cup D_{i,j})$ is not possible. Since $C_k\cup C_i = Idc(C,R'_i\cup R_j\cup D_{i,j})\neq C$ we have from Lemma \ref{lemma:combined_lemma}, Point \ref{lemma:wc_intersection_is_C}, that $C_k\cup C_i$ cannot be isostatic.
    By Lemma~\ref{lem:pinned_union_intersection}, it must be underconstrained,
    so one of $C_i$ and $C_k$ must be an edge, contradicting the assumption that both $C_i$ and $C_k$ are isostatic.

    \item 1 case: $C_k=Idc(C,R'_i\cup R'_j\cup D'_{i,j})$ is not possible. The proof is similar to the previous case.

    \item 2 cases: $C_k=Idc(C,R'_i\cup R_j\cup D'_{i,j})$ and $C_k=Idc(C,R_i\cup R'_j\cup D'_{i,j})$ are not possible.
    The proof is similar to the previous case.
\end{itemize}

>>>>

\section{Proofs}
\label{sec:appendix:a}
\label{sec:appendix:proofs}

@@

% \subsubsection{Proof of Theorem \ref{theorem:main}}
% \label{theorem:main:proof}

@@

For (4), because subgraphs of a isostatic graph can only be trivial, under\addin{constrained}, or isostatic, all cases have already been exhausted.
\end{proof}

@@

For convenience, it is implied that all graphs are the induced graph on $C$.

% The notation $Idc(G,X)$ is the subgraph of $G$ induced by the vertex set $X\subseteq V$. For a subgraph $H=(W,F)$ of $G$, $Idc(G,H)=Idc(G,W)$.

\newcommand{\inducedOnC}[1]{#1}
% \newcommand{\inducedOnC}[1]{Idc\left(C,#1\right)}

@@

% \subsubsection{Proof of Theorem \ref{theorem:algo_complexity}}

@@

% \subsubsection{Proof of Theorem \ref{theorem:omdk}}

\subsubsection{Proof of Theorem \ref{theorem:criterionc}}
\begin{proof}
    The Cartesian realization space of $(H,\left<\delta_{E'}, \lambda_F\right>)$ is computed easily with a DR-plan of size 2, and is the union of $2^t$ solutions (modulo orientation preserving isometries) each with a distinct orientation type, where $t$ is the number of triangles in the 2-tree $H$; here $\delta_{S}$ is the restriction of the length vector $\delta$ to the edges in $S$. A desired solution $p$ (or connected component of a solution space) of $(G,\delta)$ of an orientation type $\sigma_p$ can be found by a subdivided binary search   of the Cartesian realization space of $(H, \left<\delta_{E'}, \lambda_F\right>)$ of orientation type $\sigma_p$ - as $\lambda_F$ ranges over the discretized convex polytope $\Phi_F(G',\delta_E')$ with bounding hyperplanes described in Theorem \ref{theorem:convexcayley}. A solution $p$ is found  when the lengths for nonedges in $D$ match $\delta_D$.
\end{proof}

@@

\subsubsection{Proof of Theorem \ref{thm:1dofcase}}
\begin{proof}
    Suppose we are given a body-pin graph and its corresponding body-bar graph $G$ and have obtained the 1-dof DR-plan $T$. Each node of $T$ will then be a vertex maximal proper 1-dof sub-graph of $G$.

@@

\begin{proof} %[Proof of Lemma~\ref{lemma:wc_intersection_makes_all_wc} for 2D pinned line incidence graphs]
We use the same notations as in the original proof of Lemma \ref{lemma:combined_lemma}, Point \ref{lemma:wc_intersection_makes_all_wc}, in the last section.
For convenience, it is implied that all graphs are the induced graph on $C$.

@@

\newcommand{\inducedOnC}[1]{#1}
% \newcommand{\inducedOnC}[1]{Idc\left(C,#1\right)}

Then we analyze all the possible cases for $C_k$.
\begin{itemize}
    \item 1 case: $C_k=\inducedOnC{R'_i\cup R'_j\cup D_{i,j}}$ is not possible. Since $C_k\cup C_i = \inducedOnC{R'_i\cup R_j\cup D_{i,j}}\neq C$ we have from Lemma \ref{lemma:combined_lemma}, Point \ref{lemma:wc_intersection_is_C}, that $C_k\cup C_i$ cannot be isostatic.
    By Lemma~\ref{lem:pinned_union_intersection}, it must be underconstrained,
    so one of $C_i$ and $C_k$ must be an edge, contradicting the assumption that both $C_i$ and $C_k$ are isostatic.

    \item 1 case: $C_k=\inducedOnC{R'_i\cup R'_j\cup D'_{i,j}}$ is not possible. The proof is similar to the previous case.

    \item 2 cases: $C_k=\inducedOnC{R'_i\cup R_j\cup D'_{i,j}}$ and $C_k=\inducedOnC{R_i\cup R'_j\cup D'_{i,j}}$ are not possible.
    The proof is similar to the previous case.
\end{itemize}

### 2015-02-21 doc/GMP2015/revision_1/img/tikz/demo_graph_clustmindrp.tikz.tex
Finished and submitted revision 1.

% LEVEL 2
    \def\x{0}
    \def\y{0}
    % \node[c] (n1va) at (\x+0, \y+0)     [label={left, inner sep=.555}:$a$]{};
    \node[c] (n1vb) at (\x-.5,\y-.866)  [label={left, inner sep=.555}:$b$]{};
    \node[c] (n1vc) at (\x+.5,\y-.866)  [label={right,inner sep=.555}:$c$]{};
    \node[c] (n1vd) at (\x-1, \y-1.732) [label={left, inner sep=.555}:$d$]{};
    \node[c] (n1ve) at (\x+0, \y-1.732) [label={below,inner sep=.555}:$e$]{};
    \node[c] (n1vf) at (\x+1, \y-1.732) [label={right,inner sep=.555}:$f$]{};
    % \tedge{n1va}{n1vb}{solid}{}{};
    \tedge{n1vb}{n1vc}{solid}{}{};
    % \tedge{n1vc}{n1va}{solid}{}{};
    \tedge{n1vb}{n1vd}{solid}{}{};
    \tedge{n1vd}{n1ve}{solid}{}{};
    \tedge{n1ve}{n1vb}{solid}{}{};
    \tedge{n1vc}{n1vf}{solid}{}{};
    \tedge{n1vf}{n1ve}{solid}{}{};
    \tedge{n1ve}{n1vc}{solid}{}{};

    \def\x{2.5}
    \def\y{-.866}
    \node[c] (n1va) at (\x+0, \y+0)     [label={left, inner sep=.555}:$a$]{};
    \node[c] (n1vb) at (\x-.5,\y-.866)  [label={left, inner sep=.555}:$b$]{};
    \tedge{n1va}{n1vb}{solid}{}{};

    \def\x{3.5}
    \def\y{-.866}
    \node[c] (n1va) at (\x+0, \y+0)     [label={left, inner sep=.555}:$a$]{};
    \node[c] (n1vc) at (\x+.5,\y-.866)  [label={right,inner sep=.555}:$c$]{};
    \tedge{n1vc}{n1va}{solid}{}{};

% LEVEL 3
    \def\x{0}
    \def\y{.5-2.35}
    % \node[c] (n1va) at (\x+0, \y+0)     [label={left, inner sep=.555}:$a$]{};
    \node[c] (n1vb) at (\x-.5,\y-.866)  [label={left, inner sep=.555}:$b$]{};
    \node[c] (n1vc) at (\x+.5,\y-.866)  [label={right,inner sep=.555}:$c$]{};
    \node[c] (n1vd) at (\x-1, \y-1.732) [label={left, inner sep=.555}:$d$]{};
    \node[c] (n1ve) at (\x+0, \y-1.732) [label={below,inner sep=.555}:$e$]{};
    % \node[c] (n1vf) at (\x+1, \y-1.732) [label={right,inner sep=.555}:$f$]{};
    % \tedge{n1va}{n1vb}{solid}{}{};
    \tedge{n1vb}{n1vc}{solid}{}{};
    % \tedge{n1vc}{n1va}{solid}{}{};
    \tedge{n1vb}{n1vd}{solid}{}{};
    \tedge{n1vd}{n1ve}{solid}{}{};
    \tedge{n1ve}{n1vb}{solid}{}{};
    % \tedge{n1vc}{n1vf}{solid}{}{};
    % \tedge{n1vf}{n1ve}{solid}{}{};
    \tedge{n1ve}{n1vc}{solid}{}{};

    \def\x{2}
    \def\y{.5-2.35}
    \node[c] (n1ve) at (\x+0, \y-1.732) [label={below,inner sep=.555}:$e$]{};
    \node[c] (n1vf) at (\x+1, \y-1.732) [label={right,inner sep=.555}:$f$]{};
    \tedge{n1vf}{n1ve}{solid}{}{};

    \def\x{3}
    \def\y{.5-2.35}
    \node[c] (n1vc) at (\x+.5,\y-.866)  [label={right,inner sep=.555}:$c$]{};
    \node[c] (n1vf) at (\x+1, \y-1.732) [label={right,inner sep=.555}:$f$]{};
    \tedge{n1vc}{n1vf}{solid}{}{};

% LEVEL 4
    \def\x{0}
    \def\y{.5-4.3}
    % \node[c] (n1va) at (\x+0, \y+0)     [label={left, inner sep=.555}:$a$]{};
    \node[c] (n1vb) at (\x-.5,\y-.866)  [label={left, inner sep=.555}:$b$]{};
    \node[c] (n1vc) at (\x+.5,\y-.866)  [label={right,inner sep=.555}:$c$]{};
    % \node[c] (n1vd) at (\x-1, \y-1.732) [label={left, inner sep=.555}:$d$]{};
    \node[c] (n1ve) at (\x+0, \y-1.732) [label={below,inner sep=.555}:$e$]{};
    % \node[c] (n1vf) at (\x+1, \y-1.732) [label={right,inner sep=.555}:$f$]{};
    % \tedge{n1va}{n1vb}{solid}{}{};
    \tedge{n1vb}{n1vc}{solid}{}{};
    % \tedge{n1vc}{n1va}{solid}{}{};
    % \tedge{n1vb}{n1vd}{solid}{}{};
    % \tedge{n1vd}{n1ve}{solid}{}{};
    \tedge{n1ve}{n1vb}{solid}{}{};
    % \tedge{n1vc}{n1vf}{solid}{}{};
    % \tedge{n1vf}{n1ve}{solid}{}{};
    \tedge{n1ve}{n1vc}{solid}{}{};

    \def\x{3}
    \def\y{.5-4.3}
    \node[c] (n1vb) at (\x-.5,\y-.866)  [label={left, inner sep=.555}:$b$]{};
    \node[c] (n1vd) at (\x-1, \y-1.732) [label={left, inner sep=.555}:$d$]{};
    \tedge{n1vb}{n1vd}{solid}{}{};

    \def\x{4}
    \def\y{.5-4.3}
    \node[c] (n1vd) at (\x-1, \y-1.732) [label={left, inner sep=.555}:$d$]{};
    \node[c] (n1ve) at (\x+0, \y-1.732) [label={below,inner sep=.555}:$e$]{};
    \tedge{n1vd}{n1ve}{solid}{}{};

% DRP edges
    \draw (vG)--(0,  -.75);
    \draw (vG)--(2.1,-.65);
    \draw (vG)--(3.2,-.55);

    \draw (0,  -.2-1.85)--(0,  -.75-1.85);
    \draw (0,  -.2-1.85)--(2.1,-.65-1.85);
    \draw (0,  -.2-1.85)--(3.2,-.55-1.85);

    \draw (0,  -.2-1.85-1.85)--(0,  -.75-1.85-1.85);
    \draw (0,  -.2-1.85-1.85)--(2.1,-.65-1.85-1.85);
    \draw (0,  -.2-1.85-1.85)--(3.2,-.55-1.85-1.85);

>>>>

% LEVEL 2
    \def\x{-2.5}
    \def\y{-.75}
    \node[c] (n1va) at (\x+0, \y+0)     [label={left, inner sep=.555}:$a$]{};
    \node[c] (n1vb) at (\x-.5,\y-.866)  [label={left, inner sep=.555}:$b$]{};
    \node[c] (n1vc) at (\x+.5,\y-.866)  [label={right,inner sep=.555}:$c$]{};
    \tedge{n1va}{n1vb}{solid}{}{};
    \tedge{n1vb}{n1vc}{solid}{}{};
    \tedge{n1vc}{n1va}{solid}{}{};

    \def\x{0}
    \def\y{-.75}
    \node[c] (n1vb) at (\x+0, \y+0)  [label={left, inner sep=.555}:$b$]{};
    \node[c] (n1vd) at (\x-.5,\y-.866) [label={left, inner sep=.555}:$d$]{};
    \node[c] (n1ve) at (\x+.5,\y-.866) [label={below,inner sep=.555}:$e$]{};
    \tedge{n1vb}{n1vd}{solid}{}{};
    \tedge{n1vd}{n1ve}{solid}{}{};
    \tedge{n1ve}{n1vb}{solid}{}{};

    \def\x{2.5}
    \def\y{-.75}
    \node[c] (n1vc) at (\x+0, \y+0)  [label={right,inner sep=.555}:$c$]{};
    \node[c] (n1ve) at (\x-.5,\y-.866) [label={below,inner sep=.555}:$e$]{};
    \node[c] (n1vf) at (\x+.5,\y-.866) [label={right,inner sep=.555}:$f$]{};
    \tedge{n1vc}{n1vf}{solid}{}{};
    \tedge{n1vf}{n1ve}{solid}{}{};
    \tedge{n1ve}{n1vc}{solid}{}{};

% LEVEL 3
    \def\x{-2.75}
    \def\y{-2.25}
    \node[c] (n1va) at (\x+0, \y+0)     [label={left, inner sep=.555}:$a$]{};
    \node[c] (n1vb) at (\x-.5,\y-.866)  [label={left, inner sep=.555}:$b$]{};
    \tedge{n1va}{n1vb}{solid}{}{};

    \def\x{-2.25}
    \def\y{-2.25}
    \node[c] (n1vc) at (\x+.5,\y-.866)  [label={right,inner sep=.555}:$c$]{};
%
%
    \def\x{-.25}
    \def\y{-2.25}
    \node[c] (n1vb) at (\x+0, \y+0)  [label={left, inner sep=.555}:$b$]{};
    \node[c] (n1vd) at (\x-.5,\y-.866) [label={left, inner sep=.555}:$d$]{};
    \tedge{n1vb}{n1vd}{solid}{}{};

    \def\x{.25}
    \def\y{-2.25}
    \node[c] (n1ve) at (\x+.5,\y-.866) [label={below,inner sep=.555}:$e$]{};
%
%
    \def\x{2.25}
    \def\y{-2.25}
    \node[c] (n1vc) at (\x+0, \y+0)  [label={right,inner sep=.555}:$c$]{};
    \node[c] (n1ve) at (\x-.5,\y-.866) [label={below,inner sep=.555}:$e$]{};
    \tedge{n1ve}{n1vc}{solid}{}{};

    \def\x{2.75}
    \def\y{-2.25}
    \node[c] (n1vf) at (\x+.5,\y-.866) [label={right,inner sep=.555}:$f$]{};

% DRP edges
    \draw (vG)--(-2.3,-.55);
    \draw (vG)--( 0,  -.55);
    \draw (vG)--( 2.3,-.55);

    \draw (-2.5-.1, -1.716)--(-2.65,-1.95);
    \draw (-2.5+.1, -1.716)--(-2.05,-2.55);

    \draw (-2.5-.1+2.5, -1.716)--(-2.65+2.5,-1.95);
    \draw (-2.5+.1+2.5, -1.716)--(-2.05+2.5,-2.55);

    \draw (-2.5-.1+2.5+2.5, -1.716)--(-2.65+2.5+2.5,-1.95);
    \draw (-2.5+.1+2.5+2.5, -1.716)--(-2.05+2.5+2.5,-2.55);

### 2015-02-21 doc/GMP2015/revision_1/s00_abstract.tex
Finished and submitted revision 1.

\begin{abstract}
A variety of quasi-uniform (aperiodic) and self-similar, layered material structures are a natural consequence of design objectives such as rigidity or flexibility, minimizing mass, optimally distributing external stresses and participating in the assembly of diverse and multifunctional, larger  structures.

Crucial for the design and analysis of the abovementioned properties is the recursive decomposition of diverse types of underlying 2D geometric constraint systems that are \vemph{isostatic or underconstrained (which we call collectively as \dfn{qusecs})}. While the optimal recursive decomposition (\dfn{DR-planning}) problem is NP-hard even for (possibly overconstrained) 2D bar-joint constraint systems we describe an \candrpcomplexity\ algorithm  for qusecs. Besides elucidating NP-hardness, the algorithm outputs \dfn{canonical} DR-plans that meet various desirable, previously studied criteria. We leverage recent results on Cayley configuration spaces to show that the indecomposable systems---that are solved at node of the optimal DR-plan by recombining solutions to child systems---can be minimally modified to become decomposable and have a small DR-plan, leading to efficient realization algorithms. We show formal connections to well-known problems such as completion of underconstrained systems. We briefly discuss the modeling and analysis of two specific 2D layered materials as applications of the above theory and algorithms. We intend to make a software implementation and videos available upon request and publicly available for the final version.
\end{abstract}

>>>>

\begin{abstract}
\cutout{A variety of quasi-uniform (aperiodic) and self-similar, layered material structures are a natural consequence of design objectives such as rigidity or flexibility, minimizing mass, optimally distributing external stresses and participating in the assembly of diverse and multifunctional, larger  structures.}

Crucial for the design and analysis of \cutout{the abovementioned properties} \addin{quasi-uniform (aperiodic) and self-similar, layered material structures} is the recursive decomposition of diverse types of underlying 2D geometric constraint systems \cutout{that are isostatic or underconstrained (} \addin{,} which we call \dfn{qusecs}\cutout{)}. While the optimal recursive decomposition (\dfn{DR-planning}) problem is NP-hard \cutout{even} for \cutout{(possibly overconstrained)} \addin{general} 2D bar-joint constraint systems\addin{,} we describe an \candrpcomplexity\ algorithm  for qusecs \addin{that are defined to be isostatic or underconstrained}. \cutout{Besides elucidating NP-hardness, the algorithm output} \addin{The algorithm relies on the new notion of a} canonical DR-plan\cutout{s} that meets various desirable, previously studied criteria. \addin{In addition,} we leverage recent results on Cayley configuration spaces to show that the indecomposable systems---that are solved at the nodes of the optimal DR-plan by recombining solutions to child systems---can be minimally modified to become decomposable and have a small DR-plan, leading to efficient realization algorithms. We show formal connections to well-known problems such as completion of underconstrained systems. We briefly discuss the modeling and analysis of two specific 2D layered materials, modeled as body-hyperpin and pinned line-incidence systems, as applications of the above theory and algorithms. We intend to make a software implementation and videos available upon request and publicly available for the final version.
\end{abstract}
